---
title: "Chapter 3 & 4 Exercises"
author: "C組  連昱婷、劉心雨、莊芸綺"
date: "2020/4/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 3
## Question 5
To rotate a vector $(x, y)^{T}$ anticlockwise by $\theta$ radians, you premultiply it by the matrix.  

```{r}
x<-matrix(c(1,0),2,1)
print(x)  #a vector
a<-floor(cos(pi/2))
b<-sin(pi/2)
m<-matrix(c(a,b,-b,a),2,2)
#print(m)
print(m%*%x)  #rotate theta = 90 degrees
```


## Question 7
How would you find the sum of every third element of a vector x?
```{r}
x<-c(1:10)
print(x)
sum<-c(3)+c(6)+c(9)
print(sum)
```

## Question 10
Write a program that uses a loop to find the minimum of a vector x, without
using any predefined functions like min(...) or sort(...).  
You will need to define a variable, x.min say, in which to keep the smallest value you have yet seen.  
Start by assigning x.min <- x[1] then use
a for loop to compare x.min with x[2], x[3], etc.  
If/when you find
x[i] < x.min, update the value of x.min accordingly. 

```{r}
x<-c(3,1,6,7,0,4)
x.min<-x[1]
for(i in 1:6)
{
  #print(x[i])
  if(x[i]<x.min)
    x.min<-x[i]  #update the value of x.min
}
print(x.min)
```

## Chapter 4
## Question 3
Devise a program that outputs a table of squares and cubes of the numbers 1 to n. For n <- 7 the output should be as follows:

```{r}
number<-c(1:7)
square<-number^2
cube<-number^3
y<-data.frame(number,square,cube)
print(y)
```

## Question 4
Write an R program that prints out the standard multiplication table:

```{r}
m1 = matrix(1:9, nrow=9, byrow=TRUE)
m2 = matrix(1:9, nrow=1, byrow=TRUE)
print(m1%*%m2) #matrix multiplication
```

## Question 5
Use R to plot the hyperbola $x^{2}$ − $\frac{y^{2}}{3}$ = 1
```{r}
 x <- seq(0,5, by = 0.01)
 y.upper <-  sqrt(3*x^2-3)
 y.lower <- -sqrt(3*x^2-3)
 x.max <- max(x)
 y.max <- sqrt(3)*x.max
 x.min <- -x.max
 y.min <- -y.max
 par(pty = "s")
 plot(c(x.min,x.max), c(y.min,y.max), 
      type = "n", xlab = "x", ylab = "y")
 
 lines(x, y.upper)
 lines(x, y.lower)
 lines(-x, y.upper)
 lines(-x, y.lower)
 
 segments(x.min,y.min,x.max,y.max)
 segments(x.min,y.max,x.max,y.min)
 
 points(2, 0)
 points(-2, 0)
 text(2, 0, "focus (2, 0)", pos = 4)
 text(x.max,y.max, "asymptote y = sqrt(3)*x", pos  = 2)
 title("The hyperbola x^2-y^2/3 = 1")
 
```



