---
title: "Chapter 2 Exercises"
author: "C組  連昱婷、劉心雨、莊芸綺"
date: "2020/3/20"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Give R assignment statements that set the variable z to  
   (a). $x^{a^{b}}$  
   (b). $(x^{a})^b$  
   (c). $3x^{3}+2x^{2}+6x+1$ (try to minimise the number of operations required)  
   (d). the digit in the second decimal place of x (hint: use floor(x) and/or %%)  
   (e). z + 1
```{r sqare}
#1a
b<-2
a<-3
x<-2.25
z<-x^(a^b)
z
```
   
```{r square}
#1b
b<-2
a<-3
x<-2.25
z<-(x^a)^b
z
```

```{r}
#1c
x<-2.25
z<-x*(x*(3*x+2)+6)+1  #6 operations
z
```

```{r}
#1d
#floor(z)=58
#(z-floor(z))=0.796875
z<-floor(z)+floor((z-floor(z))*100)/100
z
```

```{r}
#1e
z<-z+1
z
```


## Question 2
Give R expressions that return the following matrices and vectors  
  (a). (1, 2, 3, 4, 5, 6, 7, 8, 7, 6, 5, 4, 3, 2, 1)  
  (b). (1, 2, 2, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 5)  
  (c). $$
 \left\{
 \begin{matrix}
   0 & 1 & 1 \\
   1 & 0 & 1 \\
   1 & 1 & 0
  \end{matrix}
  \right\}$$  
  (d).$$
 \left\{
 \begin{matrix}
   0 & 2 & 3 \\
   0 & 5 & 0 \\
   7 & 0 & 0
  \end{matrix}
  \right\}$$
  
```{r}
#2a
c(1:8,7:1)
```
  
```{r}
#2b
rep(1:5,1:5)
```

```{r}
#2c
A<-matrix(1,3,3)
B<-diag(3)
A-B
```

```{r}
#2d
matrix(c(0,0,7,2,5,0,3,0,0),3,3)
```

## Question 3
Suppose vec is a vector of length 2. Interpreting vec as the coordinates ofa point in ($R^{2}$), use R to express it in polar coordinates. You will need (at least one of) the inverse trigonometric functions: acos(x), asin(x), and atan(x).  


```{r}
#3
vec<-c(sqrt(2),sqrt(2))
radius<-sqrt(vec[1]^2+vec[2]^2)
radius

x<-vec[1]
y<-vec[2]
radian<-atan(y/x)
deg<-radian*180/pi  #
deg

cat(c("polar coordinates:","(",radius,",",deg,")"))


```



## Question 4
Use R to produce a vector containing all integers from 1 to 100 that are
not divisible by 2, 3, or 7.  

```{r}
#4
x<-1:100
x[(x%%2!=0)&(x%%3!=0)&(x%%7!=0)]

```


## Question 5
Suppose that queue <- c("Steve", "Russell", "Alison", "Liam")
and that queue represents a supermarket queue with Steve first in line.
Using R expressions update the supermarket queue as successively:  
  (a). Barry arrives;  
  (b). Steve is served;  
  (c). Pam talks her way to the front with one item;  
  (d). Barry gets impatient and leaves;  
  (e). Alison gets impatient and leaves.  
  
  For the last case you should not assume that you know where in the queue Alison is standing.  
  Finally, using the function which(x), find the position of Russell in the queue.  
  Note that when assigning a text string to a variable, it needs to be in quotes.  
  We formally introduce text in Section 4.1.


```{r}
#5a:Barry arrives
queue<-c("Steve","Russell","Alison","Liam")
queue<-c(queue,"Barry")
cat(queue)
```

```{r}
#5b:Steve leaves
queue<-c(queue[-1])
cat(queue)
```

```{r}
#5c:Pam arrives
queue<-c("Pam",queue)
cat(queue)
```

```{r}
#5d:Barry leaves
queue<-c(queue[1:4])
cat(queue)
```

```{r}
#5e:Alison leaves
queue<-c(queue[-3])
cat(queue)

#the position of Russell in queue
which(queue=="Russell")
```

## Question 6
Which of the following assignments will be successful?  
What will the vectors x, y, and z look like at each stage?  
rm(list = ls())  
x <- 1  
x[3] <- 3  
y <- c()  
y[2] <- 2  
y[3] <- y[1]  
y[2] <- y[4]  
z[1] <- 0

```{r}
rm(list = ls()) #removes all objects in the workspace 
x <- 1  
x[3] <- 3  
y <- c()  
y[2] <- 2  
y[3] <- y[1]  
y[2] <- y[4]  
#z[1] <- 0  Error
```

```{r}
rm(list = ls()) #removes all objects in the workspace 
x <- 1  
x[3] <- 3  
y <- c()  
y[2] <- 2  
y[3] <- y[1]  
y[2] <- y[4]  
z <- c()  #constructs vector z
z[1] <- 0  
x
y
z
```




