---
title: "Chapter 9 Exercises"
author: "Iris"
date: "2020/4/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

In single precision four bytes are used to represent a floating point number:  
1 bit is used for the sign, 8 for the exponent, and 23 for the mantissa.  
What are the largest and smallest non-zero positive numbers in single precision (including denormalised numbers)?  
In base 10, how many significant digits do you get using single precision?  

```{r}

```

## Question 2

What is the relative error in approximating π by 22/7?  
What about 355/113?  
```{r}
n <- 22/7
error <- abs(n-pi)/n
print(error)

m <- 355/113
error <- abs(m-pi)/m
print(error)
```

## Question 5

Show that the second formula is more efficient (requires fewer operations) but can suffer from catastrophic cancellation.  
Demonstrate catastrophic cancellation with an example sample of size n = 2.
```{r}

```


## Question 6
Horner’s algorithm for evaluating the polynomial p(x) = $a_{0} + a_{1}x+ a_{0}x_{2} +· · · + a_{n}x_{n}$  
consists of re-expressing it as $a_{0}+x(a_{1}+x(a_{2}+· · ·+x(a_{n-1}+a_{n})· · ·))$  
How many operations are required to evaluate p(x) in each form?
```{r}

```

## Question 8
Use the system.time function to compare the programs primedensity.r
and primesieve.r, given in Chapter 5.

```{r}
system.time(source("primedensity.r"))
system.time(source("primesieve.r"))
```



End of chapter 9 exercises.