---
title: "Chapter 2 Exercises"
author: "C組  連昱婷、劉心雨、莊芸綺"
date: "2020/3/20"
output: 
  html_document:  default
    
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Give R assignment statements that set the variable z to  
   (a). $x^{a^{b}}$  
   (b). $(x^{a})^b$  
   (c). $3x^{3}+2x^{2}+6x+1$ (try to minimise the number of operations required)  
   (d). the digit in the second decimal place of x (hint: use floor(x) and/or %%)  
   (e). z + 1
```{r sqare}
#1a
b<-2  #將2存入b
a<-3  #將3存入a
x<-2.25  #將2.25存入x
z<-x^(a^b)  #將計算後的值存入Z
print(z)  #輸出z的結果
```
   
```{r square}
#1b
b<-2
a<-3
x<-2.25
z<-(x^a)^b
print(z)
```

```{r}
#1c
x<-2.25
z<-x*(x*(3*x+2)+6)+1  #6 operations
print(z)
```

```{r}
#1d
#floor(z)=58,取到整數位
#(z-floor(z))=0.796875,得到小數位
z<-floor((z-floor(z))*100)%%10  #利用題目所給函數計算出z的"小數點後第二位"的值
print(z)
```

```{r}
#1e
z<-z+1  #將z+1後的值存回z,所以z現在的值為z+1
print(z)
```


## Question 2
Give R expressions that return the following matrices and vectors  
  (a). (1, 2, 3, 4, 5, 6, 7, 8, 7, 6, 5, 4, 3, 2, 1)  
  (b). (1, 2, 2, 3, 3, 3, 4, 4, 4, 4, 5, 5, 5, 5, 5)  
  (c). $$
 \begin{pmatrix}
  0 &1 &1\\ 
  1 &0 &1 \\ 
  1 &1 &0
\end{pmatrix}$$  
  (d).$$
 \begin{pmatrix}
   0 & 2 & 3 \\
   0 & 5 & 0 \\
   7 & 0 & 0
  \end{pmatrix}$$
  
```{r}
#2a
print(c(1:8,7:1))  #c(1到8,7到1)
```
  
```{r}
#2b
print(rep(1:5,1:5))  #rep(1到5,重覆1到5次)
```

```{r}
#2c
A<-matrix(1,3,3)  #數值為1的3x3矩陣,存入A
B<-diag(3)  #正對角為1的矩陣,存入B
print(A-B)
```

```{r}
#2d
print(matrix(c(0,0,7,2,5,0,3,0,0),3,3))  #輸出數值為{0,0,7,2,5,0,3,0,0}的3x3矩陣
```

## Question 3
Suppose vec is a vector of length 2. Interpreting vec as the coordinates ofa point in ($R^{2}$), use R to express it in polar coordinates.  
You will need (at least one of) the inverse trigonometric functions: 
acos(x), asin(x), and atan(x).  


```{r}
#3轉極座標
vec<-c(sqrt(2),sqrt(2))  #因題目所述向量長度為2
radius<-sqrt(vec[1]^2+vec[2]^2)  #向量兩點距離為極座標半徑r
print(radius)  #輸出半徑

x<-vec[1]  #將向量第一個點存入x
y<-vec[2]  #將向量第一個點存入y
radian<-atan(y/x)  #計算arctan,即為弧度
deg<-radian*180/pi  #將弧度轉角度
print(deg)  #輸出角度

cat(c("polar coordinates:","(",radius,",",deg,")"))  #cat()函數為輸出,與print()不同地方為不會顯示""符號


```



## Question 4
Use R to produce a vector containing all integers from 1 to 100 that are
not divisible by 2, 3, or 7.  

```{r}
#4
x<-1:100  #將1-100數列存入x
print(x[(x%%2!=0)&(x%%3!=0)&(x%%7!=0)])  #若對2取餘數不等於0->不會被整除,以此類推,&符號為且

```


## Question 5
Suppose that queue <- c("Steve", "Russell", "Alison", "Liam")
and that queue represents a supermarket queue with Steve first in line.  
Using R expressions update the supermarket queue as successively:  
  (a). Barry arrives;  
  (b). Steve is served;  
  (c). Pam talks her way to the front with one item;  
  (d). Barry gets impatient and leaves;  
  (e). Alison gets impatient and leaves.  
  
  For the last case you should not assume that you know where in the queue Alison is standing.  
  Finally, using the function which(x), find the position of Russell in the queue.  
  Note that when assigning a text string to a variable, it needs to be in quotes.  
  We formally introduce text in Section 4.1.


```{r}
#5a:Barry arrives
queue<-c("Steve","Russell","Alison","Liam")  #將這四人依序存進queue
queue<-c(queue,"Barry")  #將原先queue裡的人在後面多加Barry,再存入queue
cat(queue)  #將queue印出,cat()函數說明在第三題程式碼中最後一行
```

```{r}
#5b:Steve leaves
queue<-queue[queue!= "Steve"]  #將queue裡的人扣除Steve,再存入queue
cat(queue)  #將queue印出
```

```{r}
#5c:Pam arrives
queue<-c("Pam",queue)  #將Pam存入queue之前,再存入queue
cat(queue)  #將queue印出
```

```{r}
#5d:Barry leaves
queue<-queue[queue!= "Barry"]  #將queue裡的人扣除Steve,再存入queue
cat(queue)  #將queue印出
```

```{r}
#5e:Alison leaves
queue<-queue[queue!= "Alison"]  #將queue中第三個位置的Alison扣除,再存入queue
cat(queue)  #將queue印出
which(queue=="Russell")  #which()函數可以尋找後面括弧中條件符合的位置
```

## Question 6
Which of the following assignments will be successful?  
What will the vectors x, y, and z look like at each stage?  
rm(list = ls())  
x <- 1  
x[3] <- 3  
y <- c()  
y[2] <- 2  
y[3] <- y[1]  
y[2] <- y[4]  
z[1] <- 0

```{r}
#題目敘述
rm(list = ls()) #清空工作欄 
x <- 1  #建構x是一個/一串數字
x[3] <- 3   #將3存入x第3個位置
y <- c()  #建構y是一個向量,裡面並無數值
y[2] <- 2   #將2存入y第2個位置
y[3] <- y[1]  #將y第1個位置的值存入y第3個位置
y[2] <- y[4]  #將y第4個位置的值存入y第2個位置
#z[1] <- 0  會產生Error,因為前面並沒有建構z是數列、向量或是任何東西,所以直接將0存入z的第一個位置,並不會將0存入
```

```{r}
#顯示每一步變數變化
rm(list = ls()) #removes all objects in the workspace 
x <- 1
print(x)
x[3] <- 3 
print(x)

y <- c()  
print(y)
y[2] <- 2
print(y)
y[3] <- y[1]
print(y)
y[2] <- y[4]  
print(y)

z <- c()  #建構z是一個向量,裡面並無數值
print(z)
z[1] <- 0  #再將0存入z的第一個位置
print(z)
```

End of chpater 2 exercises.


