---
title: "Chapter 10"
author: "Iris"
date: "2020/4/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Draw a function g(x) for which the fixed-point algorithm produces the oscillating sequence 1, 7, 1, 7, . . . when started with $x_{0} = 7$.  
```{r}
rm(list = ls())
fixedpoint <- function(ftn, x0, tol = 1e-9, max.iter = 100){
  xold <- x0
  xnew <- ftn(xold)
  iter <- 1
  cat("At iteration 1 value of x is:", xnew, "\n")
  while ((abs(xnew-xold) > tol) && (iter < max.iter)) {
    xold <- xnew;
    xnew <- ftn(xold);
    iter <- iter + 1
    cat("At iteration", iter, "value of x is:", xnew, "\n")
  }
  if (abs(xnew-xold) > tol){
    cat("Algorithm failed to converge\n")
    return(NULL)
  }else{
    cat("Algorithm converged\n")
    return(xnew)
  }
}

ftn1 <- function(x) return(3*sin(x/2*pi)-4*cos(x*pi))
fixedpoint(ftn1, 7, tol = 1e-06)  #tol->計算後算到的小數位
```

## Question 3
1.Use fixedpoint to find the fixed point of $cos x$. Start with $x_{0} = 0$ as your initial guess (the answer is 0.73908513).  


```{r}
rm(list = ls())
#Chpater 10 page.5 function description:

fixedpoint <- function(ftn, x0, tol = 1e-9, max.iter = 100){
  # do first iteration
  xold <- x0
  xnew <- ftn(xold)
  iter <- 1
  cat("At iteration 1 value of x is:", xnew, "\n")
  
  # continue iterating until stopping conditions are met
  while ((abs(xnew-xold) > tol) && (iter < max.iter)) {
    xold <- xnew;
    xnew <- ftn(xold);
    iter <- iter + 1
    cat("At iteration", iter, "value of x is:", xnew, "\n")
  }
  
  # output depends on success of algorithm
  if (abs(xnew-xold) > tol){
    cat("Algorithm failed to converge\n")
    return(NULL)
  }else{
    cat("Algorithm converged\n")
    return(xnew)
  }
}

ftn1 <- function(x) return(cos(x))
fixedpoint(ftn1, 0, tol = 1e-06)
```

2,Now use newtonraphson to find the root of $cos x − x$, starting with $x_{0} = 0$ as your initial guess. 

```{r}
# Newton_Raphson algorithm for solving ftn(x)[1] == 0
newtonraphson <- function(ftn, x0, tol = 1e-9, max.iter = 100){
  # initialise
  x <- x0  # x0 is the initial guess at the root
  fx <- ftn(x)
  iter <- 0
  
  # continue iterating until stopping conditions are met
  while ((abs(fx[1]) > tol) && (iter < max.iter)){
    x <- x - fx[1]/fx[2]
    fx <- ftn(x)
    iter <- iter + 1
    cat("At iteration", iter, "value of x is:", x, "\n")
  }
  
  # output depends on success of algorithm
  if (abs(fx[1]) > tol){
    cat("Algorithm failed to converge\n")
    return(NULL)
  }else{
    cat("Algorithm converged\n")
    return(x)
  }
}

ftn4 <- function(x) {
  fx <- cos(x)-x
  dfx <- -sin(x)-1
  return(c(fx, dfx))
}
newtonraphson(ftn4, 0)


```

3.Is it faster than the fixed-point method?  

By above results, we can see that newtonraphson is faster than the fixed-point method.


## Question 4
The function fixedpoint_show.r below is a modification of fixedpoint that plots intermediate results.  
Instead of using the variables tol and max.iter to determine when the algorithm stops,   
at each step you will be prompted to enter "y" at the keyboard if you want to continue.  
There are also two new inputs, xmin and xmax, which are used to determine the range of the plot.  
xmin and xmax have defaults $x_{0}$- 1 and $x_{0}$+ 1 , respectively.

function:
```{r}
fixedpoint_show <- function(ftn, x0, xmin = x0-1, xmax = x0+1){
  x <- seq(xmin, xmax, (xmax - xmin)/200)
  fx <- sapply(x, ftn)
  plot(x, fx, type = "l", xlab = "x", ylab = "f(x)",main = "fixed point f(x) = x", col = "blue", lwd = 2)
  lines(c(xmin, xmax), c(xmin, xmax), col = "blue")
  xold <- x0
  xnew <- ftn(xold)
  lines(c(xold, xold, xnew), c(xold, xnew, xnew), col = "red")
  lines(c(xnew, xnew), c(xnew, 0), lty = 2, col = "red")
  cat("last x value", xnew, " ")
  continue <- readline("continue (y or n)? ") == "y"
  while (continue){
    xold <- xnew;
    xnew <- ftn(xold);
    lines(c(xold, xold, xnew), c(xold, xnew, xnew), col = "red")
    lines(c(xnew, xnew), c(xnew, 0), lty = 2, col = "red")
    cat("last x value", xnew, " ")
    continue <- readline("continue (y or n)? ") == "y"
  }
  return(xnew)
}
```

Use fixedpoint_show to investigate the fixed points of the following functions:  
(a). $cos(x)$ using $x_{0}=1, 3, 6$.    
(b). $exp(exp(−x))$ using $x_{0} = 2$.  
(c). $x-log(x)+exp(-x)$ using $x_{0} = 2$.  
(d). $x+log(x)-exp(-x)$ using $x_{0} = 2$.  

```{r}
#a
ftn <- function(x) return(cos(x))
fixedpoint_show(ftn, 1)  #x0=1
fixedpoint_show(ftn, 3)  #x0=3
fixedpoint_show(ftn, 6)  #x0=6
```

```{r}
#b
ftn <- function(x) return(exp(exp(-x)))
fixedpoint_show(ftn, 2)
```

```{r}
#c
ftn <- function(x) return(x-log(x)+exp(-x))
fixedpoint_show(ftn, 2)
```

```{r}
#d
ftn <- function(x) return(x+log(x)-exp(-x))
fixedpoint_show(ftn, 2)
```


## Question 5
Below is a modification of newtonraphson that plots intermediate results, analogous to fixedpoint_show above.  

function:
```{r}
newtonraphson_show <- function(ftn, x0, xmin = x0-1, xmax = x0+1){
  x <- seq(xmin, xmax, (xmax - xmin)/200)
  fx <- c()
  for (i in 1:length(x)){
    fx[i] <- ftn(x[i])[1]
  }
  plot(x, fx, type = "l", xlab = "x", ylab = "f(x)",main = "zero f(x) = 0", col = "blue", lwd = 2)
  lines(c(xmin, xmax), c(0, 0), col = "blue")
  xold <- x0
  f.xold <- ftn(xold)
  xnew <- xold - f.xold[1]/f.xold[2]
  lines(c(xold, xold, xnew), c(0, f.xold[1], 0), col = "red")
  cat("last x value", xnew, " ")
  continue <- readline("continue (y or n)? ") == "y"
  while (continue){
    xold <- xnew;
    f.xold <- ftn(xold)
    xnew <- xold - f.xold[1]/f.xold[2]
    lines(c(xold, xold, xnew), c(0, f.xold[1], 0), col = "red")
    cat("last x value", xnew, " ")
    continue <- readline("continue (y or n)? ") == "y"
  }
  return(xnew)
}
```

Use it to investigate the roots of the following functions:  
(a). $cos(x) − x$ using $x_{0}$ = 1, 3, 6  
(b). $log(x) − exp(−x)$ using $x_{0}$ = 2  
(c). $x^{3} − x − 3$ using $x_{0}$ = 0  
(d). $x^{3} − 7x^{2} + 14x − 8$ using $x_{0}$ = 1.1, 1.2, . . ., 1.9  
(e). $log(x) exp(−x)$ using $x_{0} = 2$.  

```{r}
#a
ftn <- function(x) {
  fx <- cos(x)-x
  dfx <- -sin(x)-1
  return(c(fx, dfx))
}
newtonraphson_show(ftn, 1)  #x0=1
newtonraphson_show(ftn, 3)  #x0=3
newtonraphson_show(ftn, 6)  #x0=6
```

```{r}
#b
ftn <- function(x) {
  fx <- log(x)-exp(-x)
  dfx <- 1/x+exp(-x)
  return(c(fx, dfx))
}
newtonraphson_show(ftn, 2)
```

```{r}
#c
ftn <- function(x) {
  fx <- x^{3}-x-3
  dfx <- 3*x^{2}-1
  return(c(fx, dfx))
}
newtonraphson_show(ftn, 0)
```

```{r}
#d
ftn <- function(x) {
  fx <- x^{3}-7*x^{2}+14*x-8
  dfx <- 3*x^{2}-14*x+14
  return(c(fx, dfx))
}
newtonraphson_show(ftn, 1.1)  #x0=1.1
newtonraphson_show(ftn, 1.2)  #x0=1.2
newtonraphson_show(ftn, 1.3)  #x0=1.3
newtonraphson_show(ftn, 1.4)  #x0=1.4
newtonraphson_show(ftn, 1.5)  #x0=1.5
newtonraphson_show(ftn, 1.6)  #x0=1.6
newtonraphson_show(ftn, 1.7)  #x0=1.7
newtonraphson_show(ftn, 1.8)  #x0=1.8
newtonraphson_show(ftn, 1.9)  #x0=1.9

```

```{r}
#e
ftn <- function(x) {
  fx <- log(x)*exp(-x)
  dfx <- 1/x*exp(-x)-log(x)*exp(-x)
  return(c(fx, dfx))
}
newtonraphson_show(ftn, 2)
```

## Question 6
Write a program, using both newtonraphson.r and fixedpoint.r for guidance, to implement the secant root-finding method:  
$x_{n+1}=x_{n}-f(x)\frac{x_{n}-x_{n-1}}{f(x_{n})-f(x_{n-1})}$  
First test your program by finding the root of the function $cos x − x$.  
Next see how the secant method performs in finding the root of $log x − exp(−x)$ using $x_{0}$ = 1 and $x_{1}$ = 2.  
Compare its performance with that of the other two methods.  
Write a function secant_show.r that plots the sequence of iterates produced by the secant algorithm.


```{r}
#fixedpoint
fixedpoint_show <- function(ftn, x0, xmin = x0-1, xmax = x0+1){
  x <- seq(xmin, xmax, (xmax - xmin)/200)
  fx <- sapply(x, ftn)
  plot(x, fx, type = "l", xlab = "x", ylab = "f(x)",main = "fixed point f(x) = x", col = "blue", lwd = 2)
  lines(c(xmin, xmax), c(xmin, xmax), col = "blue")
  xold <- x0
  xnew <- ftn(xold)
  lines(c(xold, xold, xnew), c(xold, xnew, xnew), col = "red")
  lines(c(xnew, xnew), c(xnew, 0), lty = 2, col = "red")
  cat("last x value", xnew, " ")
  continue <- readline("continue (y or n)? ") == "y"
  while (continue){
    xold <- xnew;
    xnew <- ftn(xold);
    lines(c(xold, xold, xnew), c(xold, xnew, xnew), col = "red")
    lines(c(xnew, xnew), c(xnew, 0), lty = 2, col = "red")
    cat("last x value", xnew, " ")
    continue <- readline("continue (y or n)? ") == "y"
  }
  return(xnew)
}

ftn1 <- function(x) return(3*sin(x/2*pi)-4*cos(x*pi))
fixedpoint(ftn1, 7, tol = 1e-06)
```

```{r}
#newtonraphson
newtonraphson <- function(ftn, x0, tol = 1e-9, max.iter = 100){
  x <- x0
  fx <- ftn(x)
  iter <- 0
  while ((abs(fx[1]) > tol) && (iter < max.iter)){
    x <- x - fx[1]/fx[2]
    fx <- ftn(x)
    iter <- iter + 1
    cat("At iteration", iter, "value of x is:", x, "\n")
  }
  if (abs(fx[1]) > tol){
    cat("Algorithm failed to converge\n")
    return(NULL)
  }else{
    cat("Algorithm converged\n")
    return(x)
  }
}

ftn4 <- function(x) {
  fx <- cos(x)-x
  dfx <- -sin(x)-1
  return(c(fx, dfx))
}
newtonraphson(ftn4, 0)
```

## Question 9
For $f : R → R$, the Newton-Raphson algorithm uses a sequence of linear approximations to $f$ to find a root.  
What happens if we use quadratic approximations instead?  
Suppose that $x_{n}$ is our current approximation to $f$, then a quadratic approximation to $f$ at xn is given by the second-order Taylor expansion:
$f(x) ≈ g_{n}(x) = f(x_{n} + (x − x_{n})f′(x_{n}) + \frac{1}{2}(x − x_{n})^{2}f′′(x_{n})$.  
Let $x_{n+1}$ be the solution of $g_{n}(x) = 0$ that is closest to xn, assuming a solution exists.  
If $g_{n}(x) = 0$ has no solution, then let $x_{n+1}$ be the point at which gn attains either its minimum or maximum.

```{r}

```




End of chpater 10 exercises.
