---
title: "Chapter 11 Exercises"
author: "C組 連昱婷、劉心雨、莊芸綺"
date: "2020/5/15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 3

The standard normal distribution function is given by
$\Phi(z)=\int_{- \infty}^{z} \frac{1}{\sqrt{2\pi}}e^{-x^{2}/2} dx$  
For $p ∈ [0, 1]$, the 100p standard normal percentage point is defined as that $z_{p}$ for which $\Phi(z_{p})=p$.  
Using the function $Phi(z)$ from Example 11.2.1, calculate $z_{p}$ for $p = 0.5, 0.95, 0.975,$ and $0.99.$  

```{r}
rm(list = ls()) # clear the workspace
source("D:/Numerical Methods/source/simpson_n.r")

phi <- function(x) return(exp(-x^2/2)/sqrt(2*pi))

Phi <- function(z) {
if (z < 0) {
  return(0.5 - simpson_n(phi, z, 0))
  } else {
  return(0.5 + simpson_n(phi, 0, z))
  }
}

simpson_n(Phi, 0, 1, 100*0.5)
simpson_n(Phi, 0, 1, 100*0.95)
simpson_n(Phi, 0, 1, 100*0.975)
simpson_n(Phi, 0, 1, 100*0.99)


```



## Question 4
Consider $I=\int_{0}^{1}\frac{3}{2}\sqrt{x}dx=1$  
Let $T_{n}$ be the approximation to $I$ given by the trapezoid rule with a partition of size $n$   
and let $S_{n}$ be the approximation given by Simpson’s rule with a partition of size $n$.  
Let $n_{T}(\epsilon )$ be the smallest value of $n$ for which $|T_{n}-I|\leq \epsilon$ and let $n_{S}(\epsilon )$ be the smallest value of $n$ for which $|S_{n}-I|\leq \epsilon$.  
Plot $n_{T}(\epsilon )$ and $n_{S}(\epsilon )$ against $\epsilon$ for $\epsilon=2^{-k}, k=2,...,16$.

```{r}
source("D:/Numerical Methods/source/trap.r")
options(digits = 16)
f2 <- function(x) return((3/2)*sqrt(x))
Tn <- trapezoid(f2, 0, 1)
#print(Tn)
for(i in 3:16){
  T <- trapezoid(f2, 0, 1, n=i)
  print(T)
  if(T < Tn){
    Tn <- T
    print(Tn)
  }
}

source("D:/Numerical Methods/source/simpson.r")
options(digits = 16)
f4 <- function(x) return((3/2)*sqrt(x))
Sn <- simpson(f4, 0, 1, tol = 1/4)
#print(Sn)
for(i in 3:16){
  S <- simpson(f4, 0, 1, tol = 2^(-i))
  print(S)
  if(S < Sn){
    Sn <- S
    print(Sn)
  }
}

```


```{r eval=FALSE, include=FALSE}
trap <- function(ftn, a, b, tol = 1e-8, verbose = FALSE) {
  I=1
  T.diff <- tol + 1
  while (S.diff > tol) {
    h <- (b-a)/n
    x.vec <- seq(a, b, by = h)
    f.vec <- sapply(x.vec, ftn)
    T <- h*(f.vec[1]/2 + sum(f.vec[2:n]) + f.vec[n+1]/2)
    T.diff <- abs(T - I)
}
if (verbose) #cat('partition size', n, '\n')
return(T)
}

```



```{r eval=FALSE, include=FALSE}
rm(list = ls()) # clear the workspace
source("D:/Numerical Methods/source/simpson_n.r")
ftn <- function(x) return(1/x)
S <- function(n) simpson_n(ftn, 0.01, 1, n)
n.vec <- seq(10, 1000, by = 10)
S.vec <- sapply(n.vec, S)
opar <- par(mfrow = c(1, 2), pty="s", mar=c(4,4,2,1), las=1)
plot(n.vec, S.vec + log(0.01), type = "l",
xlab = "n", ylab = "error")
plot(log(n.vec), log(S.vec + log(0.01)), type = "l",
xlab = "log(n)", ylab = "log(error)")
par(opar)

```

End of chpater 11 exercises.
